Intelligent Quadcopter for IARC 2018

### 2019-05-31 IARC_Paper_2019/Paper.tex
Start putting 2019 in LaTeX. Also, actually write the dang thing.

%%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
\affiliatedauthor{Noel Brownback}{\vspace{-.5cm}}
\affiliatedauthor{Anthony Carreon}{\vspace{-.5cm}}
\affiliatedauthor{Shayer Hassan}{\vspace{-.5cm}}
\affiliatedauthor{Eric Johnson}{\vspace{-.5cm}}
\affiliatedauthor{Colin Lewis}{\vspace{-.5cm}}
\affiliatedauthor{Mark Loveland}{\vspace{-.5cm}}
\affiliatedauthor{Umer Salman}{\vspace{-.5cm}}
\affiliatedauthor{Ethan Starr}{The University of Texas at Austin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7. A combination of lightweight materials and powerful propulsion optimizes flight time, while standardized flight control systems supported by a massive community enables customization and adaptation to the mission at hand. This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft. Safe development has been assured by strategic selection of components, thorough vetting of software in Software in the Loop simulation, and robust testing procedures in secure areas.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, Mission 7 requires novel solutions to deriving this critical telemetry, as GPS is forbidden. Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.

	Texas Aerial Robotics addresses these challenges by utilizing computer vision. Through computer vision, the drone has the ability to both understand its location and also track targets in real time. The drone records the data and position of the objects, simulating those which lie beyond the field of view, which allows for strategic analysis and definition based on estimates of unseen/out of sight targets. Interaction with these objectives is achieved using the carbon fiber bottom plate of the aircraft and perimeter prop guards, a material choice that lends itself to lightweight resiliency.

	\begin{figure}[!htbp]
		\begin{center}
			\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
				% Place nodes
				\node [block] (electronicsBattery) {Electonics Battery};
				\node [block, right of=electronicsBattery, xshift=2.5cm] (motorBattery) {Motor Battery};
				\node [block, below of=electronicsBattery] (siphon) {Power siphon};
				\node [block, below of=siphon] (Pixhawk) {Pixhawk};
				\node [block, below right of=electronicsBattery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
				\node [block, below left of=electronicsBattery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2s};
				\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
				\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
				\node [block, below right of=Jetson, yshift=-.5cm] (Camera) {Cameras};
				\node [block, below left of=Jetson, yshift=-.5cm] (2dLidar) {2D LiDAR};
				\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
				\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
				\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {LiDAR};
				\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
				% Draw edges
				\path [line] (electronicsBattery) -- (siphon);
				\path [line] (siphon) -- (Pixhawk);
				\path [line] (motorBattery) -- (PDB);
				\path [line] (PDB) -- (ESCs);
				\path [line] (electronicsBattery) -- (Jetson);
				\path [line, dashed] (Camera) -- (Jetson);
				\path [line, dashed] (2dLidar) -- (Jetson);
				\path [line, dashed] (Flow) -- (Pixhawk);
				\path [line, dashed] (Jetson) -- (Pixhawk);
				\path [line, dashed] (LiDAR) -- (Pixhawk);
				\path [line, dashed] (Pixhawk) -- (Telemetry);
				\path [line, dashed] (Spektrum) -- (Pixhawk);
				\path [line, dashed] (Pixhawk) -- (ESCs);
				\path [line] (ESCs) -- (Motors);
			\end{tikzpicture}
		\caption*{Flowchart of quadcopter electronics \\ \scriptsize *Solid arrows indicate power while dashed lines indicate power+data}
		\end{center}
	\end{figure}

@@

	2017 - Have a working bot, with computer vision software in working or nearly working state

	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability

\section*{AIR VEHICLE}
	\subsection*{Propulsion and Lift System}
			The vehicle utilizes an x-y axis symmetrical quad-rotor system. This provides a balanced airframe optimized for omnidirectional maneuvering. The frame is lifted by four T-Motor U3 KV700 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.

			The propellers used with the motors are 13 [in] long and made of carbon fiber. These T-Motor propellers provide excellent precision, durability, and efficiency. The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.

	\subsection*{Guidance, Navigation, and Control}
		\subsubsection*{Stability Augmentation System}
			Our system builds off of the robust open source project Arducopter. Arducopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude LiDAR, and the optical flow sensor. The Arducopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones. The vast community of developers and users ensures refined controls code with lots of features.

		\subsubsection*{Navigation}
			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin. This has been done to make our drone capable of navigating in GPS denied environments. For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LiDAR, and the optical flow sensor. The EKF position is then queried via mavros so that our strategy code can use our position to make intelligent decisions. In addition, the strategy node takes in data from computer vision and 2D LiDAR. The strategy node then determines a waypoint and mode, and the ROS controls node will do a sanity check on the waypoint and publish the waypoint until the drone has reached its destination. Over time, the EKF will have some error in comparison to reality. To combat this, the controls node will input a correction vector. This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid. This algorithm goes as follows: Gaussian blur, color threshold, erosion, dilation, Canny edge detection, Hough transform, line intersection, and non-maximum suppression.

@@

		\subsubsection*{Flight Termination System}
			Our drone houses a 40 [A] brushless ESC connected to an RC receiver, which acts as our kill switch. In the event of catastrophic failure, the safety operator can send the kill signal, and all power will be cut from the drone's systems.

\section*{PAYLOAD}
	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, an array of cameras, and 3 Nvidia Jetson TX2s. In addition, the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.

			The 1D LiDAR module used is the LIDAR-Lite v3 from Garmin. This one-dimensional sensor is directed downward and provides data that is used to determine altitude. The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction. The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses. The data from these sensors is used by the Pixhawk onboard system for flight control and maneuvering of the quadcopter.

		\subsubsection*{Mission Sensors}
			For completion of Mission 7, the drone must be able to detect Roombas and obstacles. The quadcopter is equipped with a single downward facing camera and four outward facing cameras for image recognition, as well as a two-dimensional plane LiDAR sensor for obstacle avoidance.

			The singular bottom camera is a Logitech C210 webcam. This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction. The four peripheral cameras are Logitech 960 C270s. These are used to recognize and track the Roombas around the playing field. These five webcams provide enough information to allow the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
			The 2D LiDAR sensor is the SWEEP sensor by Scanse. This is a single LiDAR that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection. We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.

@@

			\begin{figure}[!htbp]
				\begin{center}
					\includegraphics[width=0.75\textwidth]{roomba}
				\end{center}
			\end{figure}

>>>>

%%%%%%%%%%%% SET AUTHOR NAMES AND AFFILIATIONS %%%%%%%%%%%%
\affiliatedauthor{Umer Salman, Mario Gonzalez}{The University of Texas at Austin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 8. A combination of lightweight materials and powerful propulsion optimizes flight time, while standardized flight control systems supported by a massive community enables customization and adaptation to the mission at hand. This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the aiding of people to analyze and interact with an environment. This is done through homebrewed QR code decoding algorithms and the shared computing power onboard the multiple aircrafts. Safe development has been assured by strategic selection of components, thorough vetting of software in Software in the Loop simulation, and robust testing procedures in secure areas.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, Mission 8 requires novel solutions to deriving this critical telemetry as GPS is forbidden. Additionally, the aircrafts must be capable of taking commands in a humanized "natural" fashion and avoid other aircrafts without being informed of those other aircrafts' locations.

	Texas Aerial Robotics addresses these challenges by utilizing computer vision. TAR uses ORBSLAM2, an "Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras" to create maps of the arena while in flight and use that data in real time. The drone creates pointclouds of the objects in view using the stereo camera and combines sections together. This means that should a section of the map start showing drift, the ORBSLAM2/ORBSLAMM System will toss out just the section while maintaining as much of the map as possible. TAR hopes to combine the processing between the multiple drones to have them work together on one map. These drones also solve for the QR code that is the combination the human needs for collecting the objects. The drone is also built with safety for a plethora of other objects, containing man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.

	\begin{figure}[!htbp]
		\begin{center}
			\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
				\node [block] (battery) {Battery};
				\node [block, below of=battery] (siphon) {Power siphon};
				\node [block, below of=siphon] (Pixhawk) {Pixhawk};
				\node [block, below right of=battery, xshift=3cm, yshift=-.5cm, align=center] (PDB) {Power Distribution \\ Board};
				\node [block, below left of=battery, xshift=-3cm, yshift=-.7cm] (Jetson) {Nvidia Jetson TX2};
				\node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
				\node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
				\node [block, below right of=Jetson, yshift=-.5cm] (StereoCamera) {ORBSLAM stereo camera};
				\node [block, below of=Jetson, yshift=-.5cm] (DownCamera) {Downward camera};
				\node [block, below left of=Jetson, yshift=-.5cm] (Sonars) {4 sonar distance sensors};
				\node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
				\node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
				\node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LiDAR) {Downward rangefinder (ToF)};
				\node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
				% Draw edges
				\path [line] (battery) -- (siphon);
				\path [line] (siphon) -- (Pixhawk);
				\path [line] (battery) -- (PDB);
				\path [line] (PDB) -- (ESCs);
				\path [line] (battery) -- (Jetson);
				\path [line, dashed] (StereoCamera) -- (Jetson);
				\path [line, dashed] (DownCamera) -- (Jetson);
				\path [line, dashed] (Sonars) -- (Jetson);
				\path [line, dashed] (Flow) -- (Pixhawk);
				\path [line, dashed] (Jetson) -- (Pixhawk);
				\path [line, dashed] (LiDAR) -- (Pixhawk);
				\path [line, dashed] (Pixhawk) -- (Telemetry);
				\path [line, dashed] (Spektrum) -- (Pixhawk);
				\path [line, dashed] (Pixhawk) -- (ESCs);
				\path [line] (ESCs) -- (Motors);
			\end{tikzpicture}
		\caption*{Flowchart of quadcopter electronics \\ \scriptsize *Solid arrows indicate power while dashed lines indicate power+data}
		\end{center}
	\end{figure}

@@

	2019 - Have a working system, with localization of multiple drones working together to solve the QR code and communicate with the person through voice commands in working or nearly working state.

	2020 - Finish all aspects of mission through more networking between the quadcopters, tweak the physique of the drone for better flight control and stability, have better communication between drones to know where enemy drones are at all times, add aesthetic design choices, and test for hours in gyms in as many conditions as possible,

\section*{AIR VEHICLE}
	\subsection*{Propulsion and Lift System}
			The vehicle utilizes an y axis symmetrical quad-rotor system. This H-frame provides a stable quadcopter for a smaller overall package while maintaining plenty of room for electronics. The frame is lifted by four T-Motor MN2212 KV920-V2.0 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 9.5 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.

			The propellers used with the motors are 9.5 [in] long and made of plastic. These T-Motor propellers provide excellent precision, durability, and efficiency. The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.

	\subsection*{Guidance, Navigation, and Control}
		\subsubsection*{Stability Augmentation System}
			Our system builds off of the robust open source project ArduCopter. ArduCopter, which runs on the Pixhawk, controls the stability of the drone by taking in data from the IMU, compass, altitude ToF, and the optical flow sensor. The ArduCopter flight stack is maintained by hundreds of developers from around the world and the software is deployed on thousands of commercial and recreational drones. The vast community of developers and users ensures refined controls code with lots of features.

		\subsubsection*{Navigation}
			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin. This has been done to make our drone capable of navigating in GPS denied environments. For general waypoint navigation, the drone utilizes the ArduCopter EKF that takes in data from the IMU, compass, altitude ToF, and the optical flow sensor. The EKF position is then queried via mavros so that our controls code can use our position to make intelligent decisions. In addition, the controls node takes in data from computer vision and the sonar sensors. The controls node determines a waypoint and mode, then does a sanity check on the waypoint before publishing the waypoint until the drone has reached its destination. Over time, the EKF will have some error in comparison to reality. However, using ORBSLAMM, an open-source version of ORBSLAM that contains multimapping, we are able to combat this by correcting the maps through physical objects (which will not be moving), which is then used to correct the EKF.

@@

		\subsubsection*{Flight Termination System}
			We will be using ArduCopter's EmergencyStop to act as our killswitch. In the event of catastrophic failure, the safety operator can send the kill signal, and all power will immediately be cut from the drone's ESCs, and in turn, the motors.

\section*{PAYLOAD}
	The drone has been designed to carry all the necessary GNC sensors, an array of sonar sensors, a stereo camera, a downward camera, and a Nvidia Jetson TX2. In addition, the drone carries a telemetry radio, WiFi antennas, and an RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.

			The 1D LiDAR module used is a Time of Flight (ToF) sensor named the Teraranger One. This one-dimensional sensor is directed downward and provides data to determine altitude. The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring the distance traveled and direction. The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses. The data from these sensors is used by the Pixhawk onboard system for flight control and maneuvering of the quadcopter.

		\subsubsection*{Mission Sensors}
			For completion of Mission 8, the drone must be able to detect the QR code and avoid obstacles, both moving and non-moving. The quadcopter is equipped with a single downward facing camera for reading the quadrant of the QR code. A stereo camera is used for ORBSLAMM for localization. There is also an array of sonar sensors for obstacle avoidance.

			The singular bottom camera is a ELP webcam. This webcam is used for reading the QR code quadrant. The stereo camera in front is also an ELP camera. These cameras were chosen for their very light weight while still allowing adjustment of exposure and other parameters to better read a QR code on an iPad. 
			The array of sonar sensors contains 4 MAXBOTICS 7m I2C sonars. These allow the drone to detect objects on the sides the quadcopter intends to move in. We chose to use this for obstacle detection rather than a 2D LiDAR or webcams to save on weight, space, and computing power. Sonar sensors are very tried and true. Additionally, we opted for sonar rather than radar as radar has a harder time picking up smaller objects, like a drone.

@@

			%\begin{figure}[!htbp]
			%	\begin{center}
			%		\includegraphics[width=0.75\textwidth]{roomba}
			%	\end{center}
			%\end{figure}
